Making Sequential Programs Deterministic

### 2019-03-24 design.tex
Avoid label duplication
design background todo

\todo{Need some background around here about what a type qualifier is,
  how it is represented in Java, and how to read a type \<@Q BaseType>.}

@@

\subsection{Polymorphism extensions}\label{polymorphism}

>>>>

%\todo{Need some background around here about what a type qualifier is,
%  how it is represented in Java, and how to read a type \<@Q BaseType>.}

A \textit{type} serves as an abstraction for the set of acceptable values for any expression.
A \textit{type qualifier} on a \textit{type} adds additional constraints on the values represented by that \textit{type}.
A compile time type checker can verify the correctness of this \textit{type} with its dataflow analysis and subtyping rules.
In Java, a type qualifier is written as an annotation. The type \<Integer> represents positive and negative integers besides zero.
A program analysis developer could design a type system that differentiates positive integers from the negative ones with type qualifiers
\<@Positive> and \<@Negative>.  The type \<@Positive Integer> now represents only positive values and the dataflow analysis ensures that
any negative integer value flowing into this type is reported as an error.

@@

\subsection{Polymorphism extensions}\label{polymorphism-extensions}
